### 2024-10-20 src/Submission.Rnw
Fixed merge errors

\section{Maximum Likelihood Estimation (MLE)}

<<echo=TRUE>>=
head(ddat)

@@

\section{Likelihood Ratio Test}

>>>>

\section{Maximum Likelihood Estimation (MLE)}
<<echo=TRUE>>=
head(ddat)

@@

\section{Likelihood Ratio Test}
<<echo=TRUE>>=
# Fitting Model 1: Progression ~ BMI
model1 <- lm(target ~ bmi, data = ddat)

# Fitting Model 2: Progression ~ BMI + Age
model2 <- lm(target ~ bmi + age, data = ddat)

# Summarise the models
summary(model1)
summary(model2)

# Extract the log-likelihood for both models
logLik_model1 <- logLik(model1)
logLik_model2 <- logLik(model2)

# Print the log-likelihoods (optional)
logLik_model1
logLik_model2

# Calculate the likelihood ratio test statistic
LRT_stat <- 2 * (logLik_model2 - logLik_model1)

# Degrees of freedom is the difference in the number of parameters
df <- df.residual(model1) - df.residual(model2)

# Compute the p-value for the test
p_value <- pchisq(LRT_stat, df = df, lower.tail = FALSE)

# Print the result
cat("Likelihood Ratio Test Statistic:", LRT_stat, "\n")
cat("p-value:", p_value, "\n")
@
